sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-02 doc/paper-jss/owls.Rmd
Ref apps
saved optimized file instead of original

# Example: spatially varying effect on owl counts

@@

```{r cache-negb2-2, echo=FALSE, eval=!rds_saved2}
saveRDS(fit_owl, here::here("data/snow_w_main_effect_0_150km2.rds"))
```

>>>>

# Example: spatially varying effect on owl counts {#app:owls}

@@

```{r cache-negb2-2, echo=FALSE, eval=!rds_saved2}
saveRDS(fit_owl2, here::here("data/snow_w_main_effect_0_150km2.rds"))
```
